Solar wind prediction for the Solar Probe Plus orbit

### 2017-04-05 paperMVVB_backup_2017-03-31/sections/content.tex
new date version

plot of SPP's estimated solar wind environment from predicted SSN (Fig.~\ref{fig:SPP_orbit_sw_forecast_BVNT_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_orbit_sw_forecast_BVNT_plot.png}}
	\caption{Estimated B-field median and frequency distribution during the mission time period 2024--2025.}
	\label{fig:SPP_orbit_sw_forecast_BVNT_plot}
\end{figure}
zoom into first perihelion (new figure...)\\

% The extrapolation of the general solar wind model of the SPP orbit range is plotted in Fig.~\ref{fig:sw_model_extrapolation_4_paper_plot}.\\
% \begin{figure*}
% 	{\includegraphics[width=17cm]{figures/sw_model_extrapolation_4_paper_plot.pdf}}
% 	\caption{Extrapolated solar wind parameters in the SPP observation range (\SIrange{0.0459}{0.25}{\au}). The median, mean and \SI{95.45}{\percent} range are extrapolated from the general solar wind model. use color scaled plot?}
% 	\label{fig:sw_model_extrapolation_4_paper_plot}
% \end{figure*}

\subsection{Near-Sun extrapolation behavior/effects}

The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\

>>>>

plot of SPP's estimated solar wind environment from predicted SSN; zoom into first and nearest perihelion (Fig.~\ref{fig:SPP_perihelia_prediction_plot})\\
\begin{figure}
	\resizebox{\hsize}{!}{\includegraphics{figures/SPP_perihelia_prediction_plot.pdf}}
	\caption{Estimated B-field median during the first and nearest perihelia in 2018 and 2024.}
	\label{fig:SPP_perihelia_prediction_plot}
\end{figure}

\subsection{Near-Sun extrapolation behavior/effects}
The extrapolation distance is only about one third of the model range, but as the parameters follow exponential change, one has to look at the logarithmic distance which is indeed one and a half times the model range.\\
